### 2024-02-14 documentation/thesis/thesis_document.tex
.

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1000 \gls{ppm}. In the end, the sensors should
also measure how uniform the magnetic field is in a completed \gls{mri}
system.

@@

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous 27 cm diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019. This innovative setup was
subsequently employed in 2020 to acquire in vivo MR images, showcasing
the practical applications of their pioneering research
\cite{OReilly2021-ep}. 2023 veröffentlichten de Vos, Remis und Webb
eine zusammenfassung zur gestaltng eines oint-of-care halbach array
low-field \gls{mri} system \cite{De_Vos2023-pb}.

@@

The Halbach magnet incorporated in this system boasts a 27cm diameter, a
B0 field strength of 50.4 mT, and an impressive homogeneity of 2400
\gls{ppm} over a 20cm diameter using smaller magnets
(\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
utilization of coil-based gradients for spatial encoding, significantly
enhancing the flexibility of image acquisition.

@@

Within the framework of the ``DeLoRI'' (Dedicated Low-field \gls{mri}
for breast) project, Fraunhofer MEVIS in Bremen is actively engaged in
crafting a compact and mobile low-field \gls{mri} unit tailored
specifically for screening purposes. As described since 1991 low-field
\gls{mri}s have evolved into a burgeoning realm of research, showcasing
substantial promise within the field of medical technology. The endeavor
by Fraunhofer MEVIS exemplifies the ongoing commitment to harnessing the
potential of low-field \gls{mri} for enhanced breast screening
applications.

@@

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, DeLoRI aims to design an open \gls{mri},
departing from the circular \gls{mri} configuration discussed in the
publication. This innovation is geared towards streamlining breast
examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation. In addition DeLoRI endeavors
to achieve heightened accuracy, striving for precision levels below 1000
\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to modify the
ring diameter to influence field homogeneity, the unique goal here is to
characterize the magnets pre-installation, allowing for proactive
assessments of homogeneity characteristics. This nuanced approach aims
to provide insights into magnetic field uniformity before the magnets
are integrated, thereby streamlining the optimization process.
Furthermore,

@@

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of 1000
\gls{ppm}. Furthermore, the study seeks to validate whether the
measuring range of these sensors appropriately corresponds to the
required field strength, ensuring their suitability for the intended
application.

@@

\begin{itemize}
\item
  Sensor Characterization: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than 1,000 \gls{ppm}? The desired outcome is a
  measurement of less than 50 \(\mu\)T at 1000 \gls{ppm}, with a
  specific focus on determining the sensors' viability for noise
  measurements.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Measure a wide range of different permanent magnets with regard to
  their systematic field strength
\item
  Automated measurement of the homogeneity of Hallbach rings with an
  accuracy of less than 1000 \gls{ppm}
\end{itemize}

@@

@@

>>>>

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1000\gls{ppm}. In the end, the sensors should
also measure how uniform the magnetic field is in a completed \gls{mri}
system.

@@

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous 27cm diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019. This innovative setup was
subsequently employed in 2020 to acquire in vivo MR images, showcasing
the practical applications of their pioneering research
\cite{OReilly2021-ep}. 2023 veröffentlichten de Vos, Remis und Webb
eine zusammenfassung zur gestaltng eines oint-of-care halbach array
low-field \gls{mri} system \cite{De_Vos2023-pb}.

@@

The Halbach magnet incorporated in this system boasts a 27cm diameter, a
B0 field strength of 50.4 mT, and an impressive homogeneity of
2400\gls{ppm} over a 20cm diameter using smaller magnets
(\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
utilization of coil-based gradients for spatial encoding, significantly
enhancing the flexibility of image acquisition.

@@

Within the framework of the \emph{DeLoRI} (Dedicated Low-field \gls{mri}
for breast) project, Fraunhofer MEVIS in Bremen is actively engaged in
crafting a compact and mobile low-field \gls{mri} unit tailored
specifically for screening purposes. As described since 1991 low-field
\gls{mri}s have evolved into a burgeoning realm of research, showcasing
substantial promise within the field of medical technology. The endeavor
by Fraunhofer MEVIS exemplifies the ongoing commitment to harnessing the
potential of low-field \gls{mri} for enhanced breast screening
applications.

@@

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, \emph{DeLoRI} aims to design an open
\gls{mri}, departing from the circular \gls{mri} configuration discussed
in the publication. This innovation is geared towards streamlining
breast examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation. In addition \emph{DeLoRI}
endeavors to achieve heightened accuracy, striving for precision levels
below 1000\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to
modify the ring diameter to influence field homogeneity, the unique goal
here is to characterize the magnets pre-installation, allowing for
proactive assessments of homogeneity characteristics. This nuanced
approach aims to provide insights into magnetic field uniformity before
the magnets are integrated, thereby streamlining the optimization
process. Furthermore,

@@

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of
1000\gls{ppm}. Furthermore, the study seeks to validate whether the
measuring range of these sensors appropriately corresponds to the
required field strength, ensuring their suitability for the intended
application.

@@

\begin{itemize}
\item
  Sensor Characterization: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than 1000\gls{ppm}? The desired outcome is a
  measurement of less than 50 \(\mu\)T at 1000\gls{ppm}, with a specific
  focus on determining the sensors' viability for noise measurements.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Measure a wide range of different permanent magnets with regard to
  their systematic field strength
\item
  Automated measurement of the homogeneity of Hallbach rings with an
  accuracy of less than 1000\gls{ppm}
\end{itemize}

@@

The developed framework is directly compatible with a variety of
magnetic field sensors without modifications, including those listed in
the table \ref{Implemented_digital_magnetic_field_sensors.csv}.

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. This selection was made for the
following reasons:

The developed framework is directly compatible with a variety of
magnetic field sensors without modifications, including those listed in
the table. For this evaluation, the sensors listed in the table were
used for sensor characterisation. This selection was made for the
following reasons:

\begin{itemize}
\tightlist
\item
  Availability of ready to use development boards
\item
  Specifications correspond to the application areas
\item
  Availability for testing
\end{itemize}

It is possible to carry out the sensor characterisation shown here for
other compatible sensors using the same procedure. Pre-configured
measurements \ref{command-line-interface} and analysis pipelines
\ref{programmable-data-processing-pipeline} are available for this
purpose.
